Model LF

### 2022-10-29 Final test.Rmd
commit

```{r}
yk_l_ds = prodk_ds * LF
unemp_r_ds = 1- (yk_ds/yk_l_ds)

lf_reg= dynlm(LF~ 1 + L(unemp_r_ds,1))
summary(lf_reg)

res_lf= residuals(lf_reg)

urca_res_lf= ur.df(res_lf, lags = 3, type = "none")
summary(urca_res_lf)

res_urca_res_lf= urca_res_lf@testreg$residuals
arpdiag(res_urca_res_lf,12)
```

@@

COMMENT> 
IDENTITY> unemp_r_ds
EQ> unemp_r_ds = 1- (yk_ds/yk_l_ds)

COMMENT> 
BEHAVIORAL> lf_test
TSRANGE 2005 3 2020 1
EQ> lf_test = theta_00 + theta_01 * TSLAG(unemp_r_ds,1)
COEFF> theta_00 theta_01
STORE> coe(101)

@@

COMMENT> 
IDENTITY> ur
EQ> ur = unemp/lf

COMMENT> 
IDENTITY> ur_ds
EQ> ur_ds = ur - (alpha_140 + alpha_141*SD1 + alpha_142*SD2 + alpha_143*SD3) + mean_ur

@@

  shock_1_model  = TIMESERIES(c(shock_1_model ),   
                           START=c(2005,2),FREQ=4),
  shock_2_model  = TIMESERIES(c(shock_2_model ),   
                           START=c(2005,2),FREQ=4),
  shock_3_model  = TIMESERIES(c(shock_3_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
   pf_shock = TIMESERIES(c(pf_shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  pm_ds_shock = TIMESERIES(c(pm_ds_shock),   
                        START=c(2005,2),FREQ=4),
  iloan_shock = TIMESERIES(c(iloan_shock),   
                        START=c(2005,2),FREQ=4),
  idep_shock = TIMESERIES(c(idep_shock),   
                        START=c(2005,2),FREQ=4),
   ibd_shock = TIMESERIES(c(ibd_shock),   
                        START=c(2005,2),FREQ=4),
  iboa_shock = TIMESERIES(c(iboa_shock),   
                        START=c(2005,2),FREQ=4),
   tax_rate1_shock = TIMESERIES(c(tax_rate1_shock),   
                        START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
  wage_ds_tt = TIMESERIES(c(wage_ds_tt),   
                        START=c(2006,1),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
   kont_h_ratio = TIMESERIES(c(kont_h_dp_person),   
                        START=c(2005,2),FREQ=4),
     kont_h = TIMESERIES(c(kont_h),   
                        START=c(2005,2),FREQ=4),
    prod_shock = TIMESERIES(c(prod),   
                        START=c(2005,2),FREQ=4),
   prod_shock = TIMESERIES(c(prod),   
                        START=c(2005,2),FREQ=4),
  d_2007q4 = TIMESERIES(c(d_2007q4),   
                        START=c(2005,2),FREQ=4),
  yk_l_ds = TIMESERIES(c(yk_l_ds),   
                        START=c(2005,2),FREQ=4),
  unemp_r_ds = TIMESERIES(c(unemp_r_ds),   
                        START=c(2005,2),FREQ=4),
  lf_test = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  lf_test1 = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  shock_lf_model = TIMESERIES(c(shock_lf_model),   
                        START=c(2005,2),FREQ=4)
)
```

@@

S_modelData$shock_lf_model = shock_lf_model

@@

wage_trim_00 = S_model$simulation$wage_trim
dp_person_00 = S_model$simulation$dp_person
max_dp_00 = S_model$simulation$max_dp
stat_tilpas_00 = S_model$simulation$stat_tilpas
stat_reg_00= S_model$simulation$stat_tilpas
tilpas_pr_00 = S_model$simulation$tilpas_pr
wage_gap1_00 = S_model$simulation$wage_gap1
wage_ds_t_00 = S_model$simulation$wage_ds_t
u_ds_00 = S_model$simulation$u_ds
yk_l_ds_00 = S_model$simulation$yk_l_ds
unemp_r_ds_00 = S_model$simulation$unemp_r_ds

@@

```{r}
plot(unemp_r_ds_00, col= "green"); lines(unemp_r_ds, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

@@

@@

# Scenario 7 All but prod

@@

```{r}
plot(((emp_06b - emp_bs7b)*1000), col= "blue", xlab= "Year", ylab= "Change in employment (people)", main= "Change in Employment");
lines(((emp_07b - emp_bs7b)*1000), col= "black");
legend("left", legend=c("All channels except productivity", "All channels except productivity"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black"));
grid()
```

>>>>

```{r}
yk_l_ds = prodk_ds * LF
ur_ds = 1- (yk_ds/yk_l_ds)# skifted

@@

COMMENT> 
IDENTITY> ur_ds
EQ> ur_ds = 1- (yk_ds/yk_l_ds)

@@

COMMENT> ur equation slettet
IDENTITY> ur_test
EQ> ur_test = unemp/lf

COMMENT> 
IDENTITY> ur
EQ> ur = ur_ds -(alpha_140 + alpha_141*SD1 + alpha_142*SD2 + alpha_143*SD3) - mean_ur

@@

  shock_1_model  = TIMESERIES(c(shock_1_model ),   
                           START=c(2005,2),FREQ=4),
  shock_2_model  = TIMESERIES(c(shock_2_model ),   
                           START=c(2005,2),FREQ=4),
  shock_3_model  = TIMESERIES(c(shock_3_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
   pf_shock = TIMESERIES(c(pf_shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  pm_ds_shock = TIMESERIES(c(pm_ds_shock),   
                        START=c(2005,2),FREQ=4),
  iloan_shock = TIMESERIES(c(iloan_shock),   
                        START=c(2005,2),FREQ=4),
  idep_shock = TIMESERIES(c(idep_shock),   
                        START=c(2005,2),FREQ=4),
   ibd_shock = TIMESERIES(c(ibd_shock),   
                        START=c(2005,2),FREQ=4),
  iboa_shock = TIMESERIES(c(iboa_shock),   
                        START=c(2005,2),FREQ=4),
   tax_rate1_shock = TIMESERIES(c(tax_rate1_shock),   
                        START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
  wage_ds_tt = TIMESERIES(c(wage_ds_tt),   
                        START=c(2006,1),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4),
   kont_h_ratio = TIMESERIES(c(kont_h_dp_person),   
                        START=c(2005,2),FREQ=4),
     kont_h = TIMESERIES(c(kont_h),   
                        START=c(2005,2),FREQ=4),
    prod_shock = TIMESERIES(c(prod),   
                        START=c(2005,2),FREQ=4),
   prod_shock = TIMESERIES(c(prod),   
                        START=c(2005,2),FREQ=4),
  d_2007q4 = TIMESERIES(c(d_2007q4),   
                        START=c(2005,2),FREQ=4),
  yk_l_ds = TIMESERIES(c(yk_l_ds),   
                        START=c(2005,2),FREQ=4),
  lf_test = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  lf_test1 = TIMESERIES(c(LF),   
                        START=c(2005,2),FREQ=4),
  shock_lf_model = TIMESERIES(c(shock_lf_model),   
                        START=c(2005,2),FREQ=4)
)
```

@@

S_modelData$ur_test = unemp/LF

@@

wage_trim_00 = S_model$simulation$wage_trim
dp_person_00 = S_model$simulation$dp_person
max_dp_00 = S_model$simulation$max_dp
stat_tilpas_00 = S_model$simulation$stat_tilpas
stat_reg_00= S_model$simulation$stat_tilpas
tilpas_pr_00 = S_model$simulation$tilpas_pr
wage_gap1_00 = S_model$simulation$wage_gap1
wage_ds_t_00 = S_model$simulation$wage_ds_t
u_ds_00 = S_model$simulation$u_ds
yk_l_ds_00 = S_model$simulation$yk_l_ds

@@

@@

plot(yk_l_ds_00, col= "green"); lines(yk_l_ds, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()
```

@@

# Scenario 7 All but prod and lf

@@

```{r}
plot(((emp_06b - emp_bs7)*1000), col= "blue", xlab= "Year", ylab= "Change in employment (people)", main= "Change in Employment");
lines(((emp_07b - emp_bs7b)*1000), col= "black");
legend("left", legend=c("All channels except productivity", "All channels except productivity"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black"));
grid()
```
